---
title: "Detailed outline"
output: rmarkdown::html_vignette
toc:
  depth: 2
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{Detailed outline}
---

```{r, echo = FALSE,eval = TRUE, warning=FALSE}
source("get_slide_data.R")
```

## Week 13

### Before class:

```{r, echo = FALSE}
knitr::kable(sldat[which(sldat$S %in% c("7a","7b","7c","7d","7e")),-3], align = "llccccc", row.names = FALSE)
```

## In class:

- Exercise 7.1

---

## Week 12

### Before class:

```{r, echo = FALSE}
knitr::kable(sldat[which(sldat$S %in% c("6e","6f")),-3], align = "llccccc", row.names = FALSE)
```

### In class:

- Theoretical review 
  - conditional and marginal predictions
  - nested random effects
  - [partial pooling (blog post)](https://www.tjmahr.com/plotting-partial-pooling-in-mixed-effects-models/)
- Analysis of chick growth curves: [SAS](https://raw.githubusercontent.com/lbelzile/statmod/master/code/60604A_random_slope.sas) and [R code](https://raw.githubusercontent.com/lbelzile/statmod/master/code/60604A_random_slope.R)


### After class: 

- [Nested versus crossed effects (optional reading)](https://errickson.net/stats-notes/vizrandomeffects.html)

---

## Week 11

### Before class:

```{r, echo = FALSE}
knitr::kable(sldat[which(sldat$S %in% c("6b","6c","6d")),-3], align = "llccccc", row.names = FALSE)
```

### In class:

- Theoretical review of mixed models
  - marginal versus conditional mean
  - model equation
  - REML versus ML (model comparison)
- [Workshop: models for CD4 counts](https://raw.githubusercontent.com/lbelzile/statmod/master/workshop/MATH60604A-workshop_cd4counts.pdf)

---

## Week 10

### Before class:

```{r, echo = FALSE}
knitr::kable(sldat[which(sldat$S %in% c("5g","5h","6a")),-3], align = "llccccc", row.names = FALSE)
```

- Restricted estimation maximum likelihood
- [Dependence graph](https://raw.githubusercontent.com/lbelzile/statmod/master/misc/DAG.png) of [different covariance models](https://raw.githubusercontent.com/lbelzile/statmod/master/misc/SAS_PROC_mixed_covmodels.pdf)
- [AR(1) model with irregular time steps](https://raw.githubusercontent.com/lbelzile/statmod/master/code/60604A_longitudinal.sas)
- [Workshop: testing restrictions](https://raw.githubusercontent.com/lbelzile/statmod/master/workshop/60604A_longitudinal_tests.txt)
- [ANOVA with unequal variance](https://raw.githubusercontent.com/lbelzile/statmod/master/code/60604A_ANOVA_unequal_var.sas)

---

## Week 9

### Before class:

```{r, echo = FALSE}
knitr::kable(sldat[which(sldat$S %in% c("5b","5c","5d","5e","5f")),-3], align = "llccccc", row.names = FALSE)
```

### In class:

- Discussion of features of longitudinal data: [example code from Rick Wicklin](https://raw.githubusercontent.com/lbelzile/statmod/master/code/60604A_longitudinal.sas)
- [Workshop: examples of longitudinal data](https://raw.githubusercontent.com/lbelzile/statmod/master/workshop/60604A_longitudinal.txt) and [a description of datasets](https://raw.githubusercontent.com/lbelzile/statmod/master/workshop/longitudinal_dataset_description.txt)
- [Transforming data from wide to long format](https://raw.githubusercontent.com/lbelzile/statmod/master/code/60604A_transpose.sas)


---

## Week 8

### Before class:

```{r, echo = FALSE}
knitr::kable(sldat[which(sldat$S %in% c("4g","4h","5a")),-3], align = "llccccc", row.names = FALSE)
```

### In class:

- [Poisson/binomial analysis for `sweden`](https://raw.githubusercontent.com/lbelzile/statmod/master/code/60604A_Poisson.sas).
- [Models for contingency tables (not covered)](https://raw.githubusercontent.com/lbelzile/statmod/master/code/60604A_contingencytable.sas)
- Rates - Exercise 4.3 (children ever born)
- Overdispersion - slides (see Exercise 4.4 for an example)

---

## Week 7

### Before class:

```{r, echo = FALSE}
knitr::kable(sldat[which(sldat$S %in% c("4d","4e","4f")),-3], align = "llccccc", row.names = FALSE)
```
- Course notes: Section 4.3 (excluding 4.3.3)


### In class:

- Review of Assignment 1
- [Logistic regression with **SAS**](https://raw.githubusercontent.com/lbelzile/statmod/master/code/60604A_logistic.sas)


---

## Week 6

### Before class:

```{r, echo = FALSE}
knitr::kable(sldat[which(sldat$S %in% c("4a","4b","4c")),-3], align = "llccccc", row.names = FALSE)
```
- Course notes: Sections 2.10, 4.1-4.2

### In class:

- Overview of the theory of generalized linear models.
- [Example of Box-Cox regression](https://raw.githubusercontent.com/lbelzile/statmod/master/code/60604A_BoxCox.sas)
- Midterm survey.

---

## Week 5


### Before class:

```{r, echo = FALSE}
knitr::kable(sldat[which(sldat$S %in% c("2h","2i")),], align = "llccccc", row.names = FALSE)
```
- Course notes: chapter 2 (sections 8 and 9)

### In class:

- Collinearity illustration with `wages85` data
- Graphical analysis of residuals for `college` data [(code)](https://raw.githubusercontent.com/lbelzile/statmod/master/code/60604A-residualanalysis.sas)
- [Workshop on diagnostic plots](https://lbelzile.github.io/MATH60604A-slides/graphicaldiagnostics.html)

---

## Week 4


### Before class:

```{r, echo = FALSE}
knitr::kable(sldat[which(sldat$S %in% c("2e","2f","2g")),-3], align = "llccccc", row.names = FALSE)
```
- Course notes: chapter 2 (section 5-7)

### In class:

- Workshop on interactions (Exercise 2.8)

## After class:

- Tests of linear hypothesis in **SAS**: [theory](https://documentation.sas.com/?docsetId=statug&docsetTarget=statug_intromod_sect043.htm&docsetVersion=14.3&locale=en), [R code](https://raw.githubusercontent.com/lbelzile/statmod/master/code/60604A-linear_hypothesis_tests.R), [**SAS** code](https://raw.githubusercontent.com/lbelzile/statmod/master/code/60604A-interactions.sas)
- Exercises 2.5-2.7

---

## Week 3


### Before class:

```{r, echo = FALSE}
knitr::kable(sldat[which(sldat$S %in% c("2d","3")),-3], align = "llccccc", row.names = FALSE)
```
- Course notes: chapter 3, chapter 2 (section 4)

### In class:

- [**R** demo](https://raw.githubusercontent.com/lbelzile/statmod/master/code/60604A-profile.R): sampling distribution of OLS, profile likelihood for individual coefficients
- [Interpretation of **SAS** output and tests for the `insurance` data](https://raw.githubusercontent.com/lbelzile/statmod/master/code/60604A-tests_linear_models.sas)
- [**Understanding Maximum Likelihood** by Kristoffer Magnusson](https://rpsychologist.com/d3/likelihood/)

## After class

- Exercise sheet 3
- [Tests as linear models](https://lindeloev.github.io/tests-as-linear/)

---

## Week 2

### Before class:

Recording 2c is optional
```{r, echo = FALSE}
knitr::kable(sldat[which(sldat$S %in% c("2a","2b","2c")),], align = "llccccc", row.names = FALSE)
```
- Course notes: chapter 2 (sections 1-3)

### In class

- Parameter interpretation (`intention` data, full model)
- EDA of the `insurance` data and construction of a linear model
- [Code to create added-variable plots](https://raw.githubusercontent.com/lbelzile/statmod/master/code/60604A-added-variable_plots.sas)
- xkcd comic strip: [Curve-fitting](https://xkcd.com/2048/)

### After class:

- Exercises 2.1-2.4

---

## Week 1

### Before class:

 
```{r, echo = FALSE}
knitr::kable(sldat[which(sldat$S %in% c("0","1a","1b","1c")),], align = "llccccc", row.names = FALSE)
```

- Course notes: chapter 1 and Appendix A
- Create an account on **SAS** onDemand 
- Complete the [Introduction to **SAS**](https://lbelzile.github.io/statmod/articles/introSAS.html)

### In class:

- Presentation and practice of pedagogical tools (Zoom / Etherpad / Wooclap / SAS onDemand)
- [Graphics workshop (group)](https://github.com/lbelzile/statmod/raw/master/workshop/graphics.zip)

### After class:

- `intro` quiz (self-assessment)
- Exercise 1.4 (a-b) with **SAS**. The whole exercise sheet may be somewhat difficult at this stage, but you should (be able to) complete it in the upcoming weeks.

### Additional readings:

- [Chapter 1 of *Data Visualization: A practical introduction* by Kieran Healy](https://socviz.co/lookatdata.html#lookatdata)
- [Permutation tests](https://www.jwilber.me/permutationtest/)
- [DataViz Cheatsheet](https://policyviz.com/2018/08/07/dataviz-cheatsheet/)
- [Chapter 7 of _**R** for Data Science_ by Garrett Grolemund and Hadley Wickham](https://r4ds.had.co.nz/)

### Other references:

- [Chapter 3 of _**R** for Data Science_ by Garrett Grolemund and Hadley Wickham](https://r4ds.had.co.nz/)
- [*Fundamentals of Data Visualization* by Claus O. Wilke](https://clauswilke.com/dataviz/)
- [Do's and don'ts of making effective graphics](https://stat545.com/effective-graphs.html)
- [Financial Times Visual Vocabulary](	https://github.com/ft-interactive/chart-doctor/tree/master/visual-vocabulary)
- [BBC R Cookbook (optional)](https://bbc.github.io/rcookbook/)
- [What's going on in this graph?](https://www.nytimes.com/2020/06/10/learning/over-60-new-york-times-graphs-for-students-to-analyze.html)